---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
body {
  background-color: #F1F0E8;
}
h2 {
  font-size: 24px;
  font-weight: bold;
}
p {
  font-family: 'Arial';
}

```

## Youtube Ad Anaylsis

The purpose of this report is to identify potential trends, features, and characteristics of YouTube advertisements shown to platform users. <br>
By analyzing patterns in skippable ads and ad lengths, we can gain insights into recent changes in YouTube's advertising policies.

```{r}
logged_data <- read.csv('https://docs.google.com/spreadsheets/d/e/2PACX-1vSF9wDfHKWAQf0DLe_zv5lr2vB0nl_AeZcDitlRMV8cPs1MCayRSPwmWsCzKnz8oVwf8-ZTuf5r4Wuv/pub?output=csv')

# Takes the read CSV data frame and renames the columns
latest_data <- logged_data %>%
  rename(ad_about = 2,
         ad_length = 3,
         number_of_ads = 4,
         skippable = 5)

ggplot(data = latest_data) +
  geom_bar(aes(x = skippable, fill = skippable)) +
  labs(title = "Number of skippable versus unskippable ads",
       x = "Ad Skippability",
       y = "Count of Ads") +
  scale_fill_manual(values = c("No" = "#C96868",
                               "Yes" = "#A5B68D")) +
  scale_y_continuous(labels = scales::comma_format(accuracy = 1),)
```

First graph shows if the single or the first of multiple ads in one session is skippable.
<br>
<br>
```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = number_of_ads, fill = number_of_ads)) +
  labs(title = "How Often Are Multiple Ads Played in One Ad Session",
       x = "Multiple Ads together",
       y = "Count of Ads") +
  scale_y_continuous(labels = scales::comma_format(accuracy = 1))

```

The second graph shows the number of ads played in a single session. Only single, double, and triple ads are measured, as higher counts are considered rare.


There may be a correlation between the two graphs, where users are able to skip multiple ads but unable to skip shorter single ads


<br>


### Summary of Ad length data
___________________________________________________________________________
Current number of Ads collected: `r nrow(latest_data)`

The mean **length** of all YouTube Ads collected is `r mean(latest_data$ad_length) * 60` which shows the average length of ads in seconds.

The **shortest** YouTube ad is `r min(latest_data$ad_length) * 60` and the **longest** is `r max(latest_data$ad_length) * 60`
